Event History Analysis for psychological time-to-event data: A tutorial in R with examples in Bayesian and frequentist workflows

### 2024-10-28 manuscript/manuscript.Rmd
update ms.

To conclude this Tutorial 2a, Figure 7 shows the model-based hazard functions for each prime type for participant 6, in trial 500, 1000, and 1500.

(ref:descr-plot7-caption) Model-based hazard functions for participant 6 in trial 500, 1000, and 1500.

@@

To conclude this Tutorial 2b, Figure 9 shows the model-based ca(t) functions for each prime type for participant 6, in trial 500, 1000, and 1500.

(ref:descr-plot9-caption) Model-based ca(t) functions for participant 6 in trial 500, 1000, and 1500.

>>>>

To conclude this Tutorial 2a, Figure 7 shows the model-based hazard functions for each prime type for participant 6, in trials 500, 1000, and 1500.

(ref:descr-plot7-caption) Model-based hazard functions for each prime type for participant 6 in trials 500, 1000, and 1500.

@@

To conclude this Tutorial 2b, Figure 9 shows the model-based ca(t) functions for each prime type for participant 6, in trials 500, 1000, and 1500.

(ref:descr-plot9-caption) Model-based ca(t) functions for each prime type for participant 6 in trials 500, 1000, and 1500.
